---
title: "Harry Potter NLP"
author: "Michael Siebel"
date: "`r date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    css: "../Rstyles.css" 
    code_folding: hide
    highlight: tango
    includes:
      in_header: "menu.html"
---

<br>

>  Model Ensembling and Classification for: <br>
>  Harry Potter and the Philosopher's Stone (1997) <br>
>  Harry Potter and the Chamber of Secrets (1998) <br>
>  Harry Potter and the Prisoner of Azkaban (1999) <br>
>  Harry Potter and the Goblet of Fire (2000) <br>
>  Harry Potter and the Order of the Phoenix (2003) <br>
>  Harry Potter and the Half-Blood Prince (2005) <br>
>  Harry Potter and the Deathly Hallows (2007)

# Bottom Line Up Front

I intend to answer the question:
<h6>"Which Harry Potter film is closest to its corresponding book?"</h6>

In this document, I built a model classifying portions of each books' text into the book that it belongs.  In the next, I will run film scripts through that model to determine how will it aligns with its corresponding book.

Classifying these books took 6 steps:

III) Structure text for 4 models

   * Description: Build 4 document term matricies (DTM) using different NLP techniques
   * Purpose: Use multiple NLP techniques in order to take advantage of each of their strengths

IV) Run 4 models

   * Description: Run 4 models independently with hyper-parameter tuning
   * Purpose: Optimize 4 models   

V) Perform stacked ensemble modeling

   * Description: Ensemble 4 bottom layer models with top layer model
   * Purpose: Take strengths of each model and minimize each model's weaknesses 

VI) Determine final model performance

   * Description: Test results of stacked model ensemble on testing data
   * Purpose: Ensure model process and outcome is generalizable

# Setup
```{r setup, results=FALSE, echo=TRUE, message=FALSE, comment=NA, warning=FALSE, tidy=TRUE} 
rm(list=ls())
gc()


library(pacman)
pacman::p_load(tidyverse, tidytext, rvest, xgboost, sentimentSetsR, caret, textTinyR, text2vec, tm, stm, SnowballC, stopwords, corpus, glue, RColorBrewer)
  
knitr::opts_chunk$set(echo=TRUE, message=FALSE, comment=NA, warning=FALSE, tidy=TRUE, results="hold", cache=TRUE, dpi=360)

# Custom functions
## Remove quotation marks
pasteNQ <- function(...) {
  output <- paste(...)
  noquote(output)
}
pasteNQ0 <- function(...) {
  output <- paste0(...)
  noquote(output)
}

## Chart Template
Grph_theme <- function() {
  theme_minimal(base_size=8) + 
  theme(legend.position="none")
}

## Clean Corpus
basicclean <- function(rawtext, contractions = TRUE) {
  
  # Set to lowercase
  rawtext <- tolower(rawtext)

  # Fix apostorphe
  rawtext <- gsub("’", "'", rawtext)

  # Remove contractions
  fix_contractions <- function(rawtext) {
    rawtext <- gsub("will not", "won't", rawtext)
    rawtext <- gsub("can't", "cannot", rawtext)
    rawtext <- gsub("can not", "cannot", rawtext)
    rawtext <- gsub("shall not", "shant", rawtext)
    rawtext <- gsub("n't", " not", rawtext)
    rawtext <- gsub("'ll", " will", rawtext)
    rawtext <- gsub("'re", " are", rawtext)
    rawtext <- gsub("'ve", " have", rawtext)
    rawtext <- gsub("'m", " am", rawtext)
    rawtext <- gsub("'d", " would", rawtext)
    rawtext <- gsub("'ld", " would", rawtext)
    rawtext <- gsub("'ld", " would", rawtext)
    rawtext <- gsub("'s", "", rawtext)
    return(rawtext)
  }
  if (contractions==TRUE) {
    rawtext <- fix_contractions(rawtext)
  }
  
  # Strip whitespace
  rawtext <- stripWhitespace(rawtext)

  return(rawtext)
}

# Remove stop words
removestopwords <- function(rawtext, remove=NULL, retain=NULL) {

  # Remove stop words
  stopwords_custom <- stopwords::stopwords("en", source = "snowball")
  stopwords_custom <- c(stopwords_custom, remove)
  stopwords_retain <- retain
  stopwords_custom <- stopwords_custom[!stopwords_custom %in% stopwords_retain]
  rawtext <- removeWords(rawtext, stopwords_custom)

  return(rawtext)
}

## Word Stemming
wordstem <- function(rawtext) {
  # Stemming words
  rawtext <- stemDocument(rawtext)

  return(rawtext)
}

## Remove Non-Alpha
removenonalpha <- function(rawtext) {
  # Remove puncutation, numbers, and other none characters
  rawtext <- removePunctuation(rawtext)
  rawtext <- removeNumbers(rawtext)
  rawtext <- gsub("[^[:alnum:]///' ]", "", rawtext)
  rawtext <- gsub("[']", "", rawtext)

  return(rawtext)
}

load("Harry_Potter_and_the_Classification_-_Documents.RData")
```


# III) Structure Text for Four Models
**Description:** Build 4 document term matricies (DTM) using different NLP techniques
**Purpose:** Use multiple NLP techniques in order to take advantage of each of their strengths
   
## Meta Data

### Sentiment Scores
```{r}
# Sentiment Scores
average <- function(x) {
  pos <- sum(x[x>0], na.rm = T)
  neg <- sum(x[x<0], na.rm = T) %>% abs()
  neu <- length(x[x==0])
  bal <- ( (pos-neg)/(pos+neg) )*100
  y <- ifelse(is.nan(bal),0,bal %>% as.numeric())
  return(y)
}

pages$Sentiment <- sapply(CleanText_w250, 
                          function(x) getSentiment(x, dictionary = "vader", 
                                                   score.type = average))
para3$Sentiment <- sapply(CleanText_p3, 
                          function(x) getSentiment(x, dictionary = "vader", 
                                                   score.type = average)) 
para1$Sentiment <- sapply(CleanText_p1, 
                          function(x) getSentiment(x, dictionary = "vader", 
                                                   score.type = average)) 
```


### Animated Writing
```{r, include=F}
# count exclamation marks
pages$Exclamation_Mark <- str_count(pages$Text, "[!]") / 
                pages$Wordcount %>%
                ifelse(is.na(.),0,.)
para3$Exclamation_Mark <- str_count(para3$Text, "[!]") / 
                para3$Wordcount %>%
                ifelse(is.na(.),0,.)
para1$Exclamation_Mark <- str_count(para1$Text, "[!]") / 
                para1$Wordcount %>%
                ifelse(is.na(.),0,.)

# count question marks
pages$Question_Mark <- str_count(pages$Text, "[?]") / 
                pages$Wordcount %>%
                ifelse(is.na(.),0,.)
para3$Question_Mark <- str_count(para3$Text, "[?]") / 
                para3$Wordcount %>%
                ifelse(is.na(.),0,.)
para1$Question_Mark <- str_count(para1$Text, "[?]") / 
                para1$Wordcount %>%
                ifelse(is.na(.),0,.)

# sentence length
pages$Declarative <- str_count(pages$Text, "[.]") / 
                pages$Wordcount %>%
                ifelse(is.na(.),0,.)
para3$Declarative <- str_count(para3$Text, "[.]") / 
                para3$Wordcount %>%
                ifelse(is.na(.),0,.)
para1$Declarative <- str_count(para1$Text, "[.]") / 
                para1$Wordcount %>%
                ifelse(is.na(.),0,.)
```


### Lead Characters
```{r}
heroes <- c("lily","james","hagrid","dumbledore","sirius","lupin","moody","slughorn","dobby","cedric","luna","tonks","mcgonagall","ginny","order of the phoenix","neville")
villians <- c("voldemort","nagini","snape","draco","lucius","umbridge","pettigrew","dementor","dementors","greyback","bellatrix","quirrell","riddle","death eaters","aragog","basilisk","dudley","vernon","petunia")

Sentiment <- c(heroes, villians)

# Page Level
for(string in Sentiment) {
  findstr <- paste0("\\b",string,"\\b")
  assign( string, ifelse(grepl(findstr,CleanText_w250),1,0) )
}
pages <- cbind(pages, sapply( Sentiment, get ) )

# Paragraph Level
for(string in Sentiment) {
  findstr <- paste0("\\b",string,"\\b")
  assign( string, ifelse(grepl(findstr,CleanText_p3),1,0) )
}
para3 <- cbind(para3, sapply( Sentiment, get ) )

for(string in Sentiment) {
  findstr <- paste0("\\b",string,"\\b")
  assign( string, ifelse(grepl(findstr,CleanText_p1),1,0) )
}
para1 <- cbind(para1, sapply( Sentiment, get ) )
```


## Topic Modeling
```{r}
# Function
stm_func <- function(train, test = NULL, top = NULL, script = NULL) {
  set.seed(2020)
  
  # Initiate results
  stm_test <- c()
  stm_top <- c()
  stm_script <- c()
  
  # Train
  train_dtm <- textProcessor(documents=train$Text, verbose=F)
  prep <- prepDocuments(train_dtm$documents, train_dtm$vocab, 
                        lower.thresh=2, verbose=F)
  stm_train <- stm(documents = prep$documents, 
                   vocab = prep$vocab,
                   K = 100,
                   prevalence = ~ lily + james + hagrid +
                                  dumbledore + sirius + lupin +
                                  moody + slughorn + dobby +
                                  cedric + luna + tonks +
                                  mcgonagall + ginny +
                                  `order of the phoenix` + neville +
                                  voldemort + nagini + snape +
                                  draco + lucius + umbridge +
                                  pettigrew + dementor + dementors +
                                  greyback + bellatrix + quirrell +
                                  riddle + `death eaters` + aragog +
                                  basilisk + dudley + vernon + petunia,
                   max.em.its = 5000, 
                   seed = 2020,
                   data = train,
                   interactions = FALSE,
                   init.type = "LDA", 
                   verbose=F)
  
  if (!is.null(test)) {
    # Test
    test_dtm <- textProcessor(documents=test$Text, verbose=F)
    prep <- prepDocuments(test_dtm$documents, test_dtm$vocab, 
                          lower.thresh=5, verbose=F)
    stm_test <- fitNewDocuments(model=stm_train,   
                                documents=prep$documents, 
                                newData=test,
                                origData=train, 
                                prevalence = ~ lily + james + hagrid +
                                               dumbledore + sirius + lupin +
                                               moody + slughorn + dobby +
                                               cedric + luna + tonks +
                                               mcgonagall + ginny +
                                               `order of the phoenix` + neville +
                                               voldemort + nagini + snape +
                                               draco + lucius + umbridge +
                                               pettigrew + dementor + dementors +
                                               greyback + bellatrix + quirrell +
                                               riddle + `death eaters` + aragog +
                                               basilisk + dudley + vernon +
                                               petunia,
                                prevalencePrior="Covariate",
                                verbose=F)
    
  } else { stm_test$theta <- "No test data provided" }
  
  
  if (!is.null(top)) {
    # Top Layer 
    top_dtm <- textProcessor(documents=top$Text, verbose=F)
    prep <- prepDocuments(top_dtm$documents, top_dtm$vocab, 
                          lower.thresh=5, verbose=F)
    stm_top <- fitNewDocuments(model=stm_train,   
                               documents=prep$documents, 
                               newData=top,
                               origData=train, 
                               prevalence = ~ lily + james + hagrid +
                                              dumbledore + sirius + lupin +
                                              moody + slughorn + dobby +
                                              cedric + luna + tonks +
                                              mcgonagall + ginny +
                                              `order of the phoenix` + neville +
                                              voldemort + nagini + snape +
                                              draco + lucius + umbridge +
                                              pettigrew + dementor + dementors +
                                              greyback + bellatrix + quirrell +
                                              riddle + `death eaters` + aragog +
                                              basilisk + dudley + vernon +
                                              petunia,
                               prevalencePrior="Covariate",
                               verbose=F)
    
  } else { stm_top$theta <- "No top layer data provided" }

  
  if (!is.null(script)) {
    # Script 
    script_dtm <- textProcessor(documents=script$Text, verbose=F)
    prep <- prepDocuments(script_dtm$documents, script_dtm$vocab, 
                          lower.thresh=5, verbose=F)
    stm_script <- fitNewDocuments(model=stm_train,   
                               documents=prep$documents, 
                               newData=script,
                               origData=train, 
                               prevalence = ~ lily + james + hagrid +
                                              dumbledore + sirius + lupin +
                                              moody + slughorn + dobby +
                                              cedric + luna + tonks +
                                              mcgonagall + ginny +
                                              `order of the phoenix` + neville +
                                              voldemort + nagini + snape +
                                              draco + lucius + umbridge +
                                              pettigrew + dementor + dementors +
                                              greyback + bellatrix + quirrell +
                                              riddle + `death eaters` + aragog +
                                              basilisk + dudley + vernon +
                                              petunia,
                               prevalencePrior="Covariate",
                               verbose=F)
    
  } else { stm_script$theta <- "No script data provided" }
    
  
  return(list(stm_train$theta, stm_test$theta, stm_top$theta, stm_script$theta))
}
```


## Bag of Words
```{r}
# Function
bow_func <- function(train_text, test_text = NULL, top_text = NULL, script_text = NULL) {
  set.seed(2020)
  
  # Initiate results
  dtm_test <- c()
  dtm_top <- c()
  dtm_script <- c()
  
  #Train
  train_text_cleaned <- train_text %>%
                        basicclean() %>%
                        removestopwords() %>%
                        wordstem() %>%
                        removenonalpha()
  
  ## IDs
  ids <- 1:length(train_text_cleaned)
  
  ## tokenize
  it_train <- itoken(train_text_cleaned, 
  				     ids = ids, 
  				     progressbar = FALSE) 
  
  ## ngrams
  vocab <- create_vocabulary(it_train, c(1,1)) 
  vocab <- prune_vocabulary(vocab, doc_proportion_min = 0.01)
  
  vectorizer <- vocab_vectorizer(vocab)
  
  ## create dtm
  dtm_train <- create_dtm(it_train, vectorizer, type="dgCMatrix")
  
    
  if (!is.null(test_text)) {
    # Test
    test_text_cleaned <- test_text %>%
                         basicclean() %>%
                         removestopwords() %>%
                         wordstem() %>%
                         removenonalpha()
    
    ## IDs
    ids <- 1:length(test_text_cleaned)
  
    ## tokenize
    it_test <- itoken(test_text_cleaned, 
    				    ids = ids, 
    				    progressbar = FALSE) 
    
    # create dtm
    dtm_test <- create_dtm(it_test, vectorizer, type="dgCMatrix")
    
  } else { dtm_test <- "No test data provided" }
  
  
  if (!is.null(top_text)) {
    # Top Layer 
    top_text_cleaned <- top_text %>%
                       basicclean() %>%
                       removestopwords() %>%
                       wordstem() %>%
                       removenonalpha()
      
    ## IDs
    ids <- 1:length(top_text_cleaned)
  
    ## tokenize
    it_top <- itoken(top_text_cleaned, 
    				    ids = ids, 
    				    progressbar = FALSE) 
    
    # create dtm
    dtm_top <- create_dtm(it_top, vectorizer, type="dgCMatrix")
    
  } else { dtm_top <- "No top layer data provided" }
  
  
  if (!is.null(script_text)) {
    # Script
    script_text_cleaned <- script_text %>%
                       basicclean() %>%
                       removestopwords() %>%
                       wordstem() %>%
                       removenonalpha()
      
    ## IDs
    ids <- 1:length(script_text_cleaned)
  
    ## tokenize
    it_script <- itoken(script_text_cleaned, 
    				    ids = ids, 
    				    progressbar = FALSE) 
    
    # create dtm
    dtm_script <- create_dtm(it_script, vectorizer, type="dgCMatrix")
    
  } else { dtm_script <- "No script data provided" }
    
  
  return(list(dtm_train, dtm_test, dtm_top, dtm_script))
}
```


## Word Embeddings
```{r}
# Function
we_func <- function(train_text, test_text = NULL, top_text = NULL, 
                   script_text = NULL, doc2vec = "sum_sqrt") {
  set.seed(20)
  
  # Initiate results
  dtm_test <- c()
  dtm_top <- c()
  dtm_script <- c()
  
  # Train
  ## Simple clean
  train_text_cleaned <- train_text %>%
                        basicclean(contractions = F) 
  
  ## Tokenize
  tokens <- word_tokenizer(train_text)

  ## create dtm
  dtm_train <- textTinyR::Doc2Vec$new(token_list = tokens, 
  							          word_vector_FILE = "glove.42B.300d.vec",
  							          copy_data = FALSE) 
  
	if (doc2vec == "sum_sqrt") {							
		dtm_train <- dtm_train$doc2vec_methods(method = "sum_sqrt", 
		                                       threads = 8)
	} else if (doc2vec == "min_max_norm") {
		dtm_train <- dtm_train$doc2vec_methods(method = "min_max_norm", 
		                                       threads = 8)
	} else if (doc2vec == "idf") {
	  ## IDs
    ids <- 1:length(train_text)
    ## tokenize
    it_train <- itoken(train_text_cleaned, 
    				   ids = ids, 
    				   progressbar = FALSE) 
    ## ngrams
    vocab <- create_vocabulary(it_train, c(1,1)) 
    ## IDF
		utl <- textTinyR::sparse_term_matrix$new(vector_data = unlist(vocab), 
		                                         file_data = NULL,
												 document_term_matrix = TRUE)
		tm <- utl$Term_Matrix(verbose=F)
		gl_term_w <- utl$global_term_weights()
		dtm_train <- dtm_train$doc2vec_methods(method = "idf", 
		                                       global_term_weights = gl_term_w, threads = 8)	
	}  
  
  
  if (!is.null(test_text)) {
    # Test
    test_text_cleaned <- test_text %>%
                         basicclean(contractions = F)
    
    ## Tokenize
    tokens <- word_tokenizer(test_text)
    
    ## create dtm
    dtm_test <- textTinyR::Doc2Vec$new(token_list = tokens, 
    							         word_vector_FILE = "glove.42B.300d.vec",
    							         copy_data = FALSE) 
    
	  if (doc2vec == "sum_sqrt") {							
	  	dtm_test <- dtm_test$doc2vec_methods(method = "sum_sqrt", 
	  	                                     threads = 8)
	  } else if (doc2vec == "min_max_norm") {
	  	dtm_test <- dtm_test$doc2vec_methods(method = "min_max_norm", 
	  	                                     threads = 8)
	  } else if (doc2vec == "idf") {
	    ### IDs
      ids <- 1:length(test_text)
      ### tokenize
      it_test <- itoken(test_text_cleaned, 
      				  ids = ids, 
      				  progressbar = FALSE) 
      ### ngrams
      vocab <- create_vocabulary(it_test, c(1,1))
      ### IDF
	  	utl <- textTinyR::sparse_term_matrix$new(vector_data = unlist(vocab), 
	  	                                         file_data = NULL,
	  											 document_term_matrix = TRUE)
	  	tm <- utl$Term_Matrix(verbose=F)
	  	gl_term_w <- utl$global_term_weights()
	  	dtm_test <- dtm_test$doc2vec_methods(method = "idf", 
                                               global_term_weights = gl_term_w, 
                                               threads = 8)
	  }
  
  } else { dtm_test <- "No test data provided" }

  
  if (!is.null(top_text)) {
    # Top layer
    top_text_cleaned <- top_text %>%
                       basicclean(contractions = F)
    
    ## Tokenize
    tokens <- word_tokenizer(top_text)
    
    ## create dtm
    dtm_top <- textTinyR::Doc2Vec$new(token_list = tokens, 
    							         word_vector_FILE = "glove.42B.300d.vec",
    							         copy_data = FALSE) 
    
	  if (doc2vec == "sum_sqrt") {							
	  	dtm_top <- dtm_top$doc2vec_methods(method = "sum_sqrt", 
	  	                                     threads = 8)
	  } else if (doc2vec == "min_max_norm") {
	  	dtm_top <- dtm_top$doc2vec_methods(method = "min_max_norm", 
	  	                                     threads = 8)
	  } else if (doc2vec == "idf") {
	    ### IDs
      ids <- 1:length(top_text)
      ### tokenize
      it_top <- itoken(top_text_cleaned, 
      				  ids = ids, 
      				  progressbar = FALSE) 
      ### ngrams
      vocab <- create_vocabulary(it_top, c(1,1))
      ### IDF
	  	utl <- textTinyR::sparse_term_matrix$new(vector_data = unlist(vocab), 
	  	                                         file_data = NULL,
	  											 document_term_matrix = TRUE)
	  	tm <- utl$Term_Matrix(verbose=F)
	  	gl_term_w <- utl$global_term_weights()
	  	dtm_top <- dtm_top$doc2vec_methods(method = "idf", 
                                         global_term_weights = gl_term_w,   
                                         threads = 8)
	  }  
    
  } else { dtm_top <- "No top layer data provided" }

  
  if (!is.null(script_text)) {
    # Script 
    script_text_cleaned <- script_text %>%
                       basicclean(contractions = F)
    
    ## Tokenize
    tokens <- word_tokenizer(script_text)
    
    ## create dtm
    dtm_script <- textTinyR::Doc2Vec$new(token_list = tokens, 
    							         word_vector_FILE = "glove.42B.300d.vec",
    							         copy_data = FALSE) 
    
	  if (doc2vec == "sum_sqrt") {							
	  	dtm_script <- dtm_script$doc2vec_methods(method = "sum_sqrt", 
	  	                                     threads = 8)
	  } else if (doc2vec == "min_max_norm") {
	  	dtm_script <- dtm_script$doc2vec_methods(method = "min_max_norm", 
	  	                                     threads = 8)
	  } else if (doc2vec == "idf") {
	    ### IDs
      ids <- 1:length(script_text)
      ### tokenize
      it_script <- itoken(script_text_cleaned, 
      				  ids = ids, 
      				  progressbar = FALSE) 
      ### ngrams
      vocab <- create_vocabulary(it_script, c(1,1))
      ### IDF
	  	utl <- textTinyR::sparse_term_matrix$new(vector_data = unlist(vocab), 
	  	                                         file_data = NULL,
	  											 document_term_matrix = TRUE)
	  	tm <- utl$Term_Matrix(verbose=F)
	  	gl_term_w <- utl$global_term_weights()
	  	dtm_script <- dtm_script$doc2vec_methods(method = "idf", 
                                         global_term_weights = gl_term_w,   
                                         threads = 8)
	  }  
    
  } else { dtm_script <- "No script data provided" }
  
  
  return(list(dtm_train, dtm_test, dtm_top, dtm_script))
}
```



## Create Four Datasets
```{r}
# Train/Test split
train <- pages[train_index, ]
test  <- pages[-train_index, ]

# Target Variables
target_test  <- test$Book

# Dataframe for results
results_test  <- tibble(Target = target_test)
num_test  <- as.factor(target_test) %>% as.numeric() - 1

# Top layer train
set.seed(2020)
up_top_train <- upsample_train(train, para3, para1)
top_train_target <- up_top_train$Book
top_num_train <- as.factor(top_train_target) %>% as.numeric() - 1

# Topic Model
## Bottom Layer
set.seed(20)
up_train <- upsample_train(train, para3, para1)
stm_train_target <- up_train$Book
stm_df <- stm_func(up_train, test, up_top_train)
stm_train <- stm_df[[1]] %>% cbind(up_train[ , c("Exclamation_Mark", 
                                                 "Question_Mark",
                                                 "Declarative", 
                                                 "Sentiment")])
stm_test  <- stm_df[[2]] %>% cbind(test[ , c("Exclamation_Mark", 
                                             "Question_Mark",
                                             "Declarative", 
                                             "Sentiment")])
## Top Layer
stm_top_train <- stm_df[[3]] %>% cbind(up_top_train[ , c("Exclamation_Mark", 
                                                         "Question_Mark",
                                                         "Declarative", 
                                                         "Sentiment")])

# Bag of Words (TF) Model
## Bottom Layer
set.seed(21)
up_train <- upsample_train(train, para3, para1)
bow_train_target <- up_train$Book
bow_dtm <- bow_func(up_train$Text, test$Text, up_top_train$Text)
bow_train <- bow_dtm[[1]] %>% text2vec::normalize("l1")
bow_test  <- bow_dtm[[2]] %>% text2vec::normalize("l1")
## Top Layer
bow_top_train <- bow_dtm[[3]] %>% text2vec::normalize("l1")


# Bag of Words (TF-IDF) Model
## Bottom Layer
set.seed(22)
up_train <- upsample_train(train, para3, para1)
bowtfidf_train_target <- up_train$Book
bowtfidf_dtm <- bow_func(up_train$Text, test$Text, up_top_train$Text)
bowtfidf_train <- bowtfidf_dtm[[1]]
bowtfidf_test  <- bowtfidf_dtm[[2]]
tfidf <- TfIdf$new()
bowtfidf_train <- fit_transform(bowtfidf_train, tfidf)
bowtfidf_test  <- transform(bowtfidf_test, tfidf)
## Top Layer
bowtfidf_top_train <- bowtfidf_dtm[[3]]
bowtfidf_top_train <- transform(bowtfidf_top_train, tfidf)


# Word Embeddings (Sum-SQRT) Model
## Bottom Layer
set.seed(23)
up_train <- upsample_train(train, para3, para1)

we_train_target <- up_train$Book
we_dtm <- we_func(up_train$Text, test$Text, 
                    up_top_train$Text, doc2vec = "sum_sqrt")
we_train <- we_dtm[[1]]
we_test  <- we_dtm[[2]]
## Top Layer
we_top_train <- we_dtm[[3]]


# Save
save(pages, para1, para3, 
     stm_func, bow_func, we_func, titles,
     stm_train_target, stm_train, stm_test, stm_top_train,
     bow_train_target, bow_train, bow_test, 
     bow_top_train,
     bowtfidf_train_target, bowtfidf_train, bowtfidf_test, tfidf, 
     bowtfidf_top_train,
     we_train_target, we_train, we_test, we_top_train,
     top_train_target, top_num_train, up_top_train,
     results_test, num_test, 
     file = "Harry_Potter_and_the_Classification_-_Structure.RData")
```


# IV) Run Four Models
**Description:** Run 4 models independently with hyper-parameter tuning
**Purpose:** Optimize 4 models

* Test 25 different versions of hyper-parameters on 4-fold cross validation
* Take best hyper-parameters and rerun on all training data 
* Repeat for each model

```{r}
load("Harry_Potter_and_the_Classification_-_Documents.RData")
load("Harry_Potter_and_the_Classification_-_Structure.RData")

# Sentiment model 
num_train <- as.factor(stm_train_target) %>% as.numeric() - 1
stm_train <- xgb.DMatrix(as.matrix(stm_train),
                         label=num_train)
stm_test  <- xgb.DMatrix(as.matrix(stm_test),
                         label=num_test)

# Bag of words TF model
num_train <- as.factor(bow_train_target) %>% as.numeric() - 1
bow_train <- xgb.DMatrix(bow_train,
                         label=num_train)
bow_test  <- xgb.DMatrix(bow_test,
                         label=num_test)

# Bag of words TF-IDF model
num_train <- as.factor(bowtfidf_train_target) %>% as.numeric() - 1
bowtfidf_train <- xgb.DMatrix(bowtfidf_train,
                              label=num_train)
bowtfidf_test  <- xgb.DMatrix(bowtfidf_test,
                              label=num_test)

# Word Embeddings (Sum-SQRT) model
num_train <- as.factor(we_train_target) %>% as.numeric() - 1
we_train <- xgb.DMatrix(we_train,
                           label=num_train)
we_test  <- xgb.DMatrix(we_test,
                           label=num_test)


# Global parameters
num_class <- 7

# cross validation
cv_tune <- function(data, iterations = 25, num_class = 7, 
                    nrounds = 5000, nfold = 3, 
                    eval_metric = "mlogloss", 
                    objective = "multi:softprob") {
  best_param = list()
  best_seednumber = 2020
  best_logloss = Inf
  best_logloss_index = 0
  
  for (i in 1:iterations) {
      param <- list(
            objective = objective,
            num_class = num_class,
            eval_metric = eval_metric,
            eta = runif(1, min = .0005, max = .2),
            max_depth = sample(3:7, 1),
            subsample = 0.95
            )
      seed.number <- sample.int(10000, 1)[[1]]
      set.seed(seed.number)          
      cross_val <- xgb.cv(data = data, param = param, 
                          verbose = F, nthread = 8, 
                          early_stopping_rounds = 7, maximize = FALSE,
                          nrounds = nrounds, nfold = nfold)
      
      eval_metrics <- cross_val$evaluation_log[, "test_mlogloss_mean"] %>%
                      as.data.frame()
      min_logloss <- min(eval_metrics)
      min_logloss_index <- which.min(unlist(eval_metrics))
      
      if (min_logloss < best_logloss) {
          best_eval <- eval_metrics
          best_logloss <- min_logloss
          best_nround <- min_logloss_index
          best_seednumber <- seed.number
          best_param <- param
      }
  }
  
  return(list(best_nround, best_param, best_eval))
}

# Results
pred_test <- data.frame(matrix(nrow=length(num_test), ncol=7*4))
pred_train <- data.frame(matrix(nrow=length(num_train), ncol=7*4))
```


## Topic Model
```{r}
# cross validation
cv_best <- cv_tune(data = stm_train)
pasteNQ("Best NRound:")
stm_nrounds <- cv_best[[1]] %>% as.numeric()
stm_nrounds
pasteNQ("Best Params:")
stm_params <- cv_best[[2]]
stm_params

# best model
stm_model <- xgboost(data=stm_train, verbose=F,
                     nrounds=stm_nrounds, param=stm_params)

# prediction
cols <- 1:7
pred_test[ , cols] <- predict(stm_model, stm_test) %>% 
                              matrix(ncol=num_class, byrow=TRUE)
results_test$STM_Label <- max.col(pred_test[ , cols])

# error and accuracy measure
results_test$STM_Label <- factor(results_test$STM_Label,
                                 labels = unique(results_test$Target))
stm_acc <- confusionMatrix(results_test$STM_Label, 
                           results_test$Target)
round( stm_acc$overall["Accuracy"], 2 )

# Graph
## Balanced Accuracy
stm_acc$byClass %>% 
  as.data.frame() %>%
  ggplot(aes(x = `Balanced Accuracy` %>% as.numeric()*100, 
             y = titles, fill = titles)) +
  geom_bar(stat = "identity") +
  xlim(0, 100) +
  labs(title="Balanced Accuracy",
       y="Book",
       x="Balanced Accuracy (%)") + 
  scale_fill_manual(values = c("#946B2D", "#0D6217", "#000A90", 
                               "#AAAAAA", "#000000", "#7F0909", "#FFC500")) +
  Grph_theme() 

## Feature Importance
importance_matrix <- xgb.importance(model = stm_model)
features_gb <- importance_matrix[1:10, ]
ggplot(features_gb, mapping=aes(x=reorder(Feature, Gain), y=Gain,
                                fill="hotpink")) + 
  coord_flip() +
  geom_bar(position="dodge",stat="identity") + 
  labs(title = "Top Ten Features",
       subtitle = "Topic Model",
       y = "Fractional Contribution",
       x = "Feature") + 
  guides(fill=FALSE) +
  Grph_theme()
```


## Bag of Words TF Model
```{r}
# cross validation
cv_best <- cv_tune(data = bow_train)
pasteNQ("Best NRound:")
bow_nrounds <- cv_best[[1]] %>% as.numeric()
bow_nrounds
pasteNQ("Best Params:")
bow_params <- cv_best[[2]]
bow_params

# best model
bow_model <- xgboost(data=bow_train, verbose=F,
                      nrounds=bow_nrounds, param=bow_params)

# prediction
cols <- 8:14
pred_test[ , cols] <- predict(bow_model, bow_test) %>% 
                              matrix(ncol=num_class, byrow=TRUE)
results_test$BoW_Label <- max.col(pred_test[ , cols])

# error and accuracy measure
results_test$BoW_Label <- factor(results_test$BoW_Label,
                                 labels = unique(results_test$Target))
bow_acc <- confusionMatrix(results_test$BoW_Label, 
                           results_test$Target)
round( bow_acc$overall["Accuracy"], 2 )

# Graph
## Balanced Accuracy
bow_acc$byClass %>% 
  as.data.frame() %>%
  ggplot(aes(x = `Balanced Accuracy` %>% as.numeric()*100, 
             y = titles, fill = titles)) +
  geom_bar(stat = "identity") +
  xlim(0, 100) +
  labs(title="Balanced Accuracy",
       y="Book",
       x="Balanced Accuracy (%)") + 
  scale_fill_manual(values = c("#946B2D", "#0D6217", "#000A90", 
                               "#AAAAAA", "#000000", "#7F0909", "#FFC500")) +
  Grph_theme()

## Feature Importance
importance_matrix <- xgb.importance(model = bow_model)
features_gb <- importance_matrix[1:10,]
ggplot(features_gb, mapping=aes(x=reorder(Feature, Gain), y=Gain, 
                                fill="green")) + 
  coord_flip() +
  geom_bar(position="dodge",stat="identity") + 
  labs(title = "Top Ten Features",
       subtitle = "Bag of Words (TF) Model",
       y = "Fractional Contribution",
       x = "Feature") + 
  guides(fill=FALSE) +
  Grph_theme()
```


## Bag of Words (TF-IDF) Model
```{r}
# cross validation
cv_best <- cv_tune(data = bowtfidf_train)
pasteNQ("Best NRound:")
bowtfidf_nrounds <- cv_best[[1]] %>% as.numeric()
bowtfidf_nrounds
pasteNQ("Best Params:")
bowtfidf_params <- cv_best[[2]]
bowtfidf_params

# best model
bowtfidf_model <- xgboost(data=bowtfidf_train, verbose=F,
                      nrounds=bowtfidf_nrounds, param=bowtfidf_params)

# prediction
cols <- 15:21
pred_test[ , cols] <- predict(bowtfidf_model, bowtfidf_test) %>% 
                              matrix(ncol=num_class, byrow=TRUE)
results_test$BoWtfidf_Label <- max.col(pred_test[ , cols])

# error and accuracy measure
results_test$BoWtfidf_Label <- factor(results_test$BoWtfidf_Label,
                                      labels = unique(results_test$Target))
bowtfidf_acc <- confusionMatrix(results_test$BoWtfidf_Label, 
                           results_test$Target)
round( bowtfidf_acc$overall["Accuracy"], 2 )

# Graph
## Balanced Accuracy
bowtfidf_acc$byClass %>% 
  as.data.frame() %>%
  ggplot(aes(x = `Balanced Accuracy` %>% as.numeric()*100, 
             y = titles, fill = titles)) +
  geom_bar(stat = "identity") +
  xlim(0, 100) +
  labs(title="Balanced Accuracy",
       y="Book",
       x="Balanced Accuracy (%)") + 
  scale_fill_manual(values = c("#946B2D", "#0D6217", "#000A90", 
                               "#AAAAAA", "#000000", "#7F0909", "#FFC500")) +
  Grph_theme() 

## Feature Importance
importance_matrix <- xgb.importance(model = bowtfidf_model)
features_gb <- importance_matrix[1:10,]
ggplot(features_gb, mapping=aes(x=reorder(Feature, Gain), y=Gain, 
                                fill="green")) + 
  coord_flip() +
  geom_bar(position="dodge",stat="identity") + 
  labs(title = "Top Ten Features",
       subtitle = "Bag of Words (TF-IDF) Model",
       y = "Fractional Contribution",
       x = "Feature") + 
  guides(fill=FALSE) +
  Grph_theme()
```


## Word Embeddings (Sum-SQRT) Model
```{r}
# cross validation
cv_best <- cv_tune(data = we_train)
pasteNQ("Best NRound:")
we_nrounds <- cv_best[[1]] %>% as.numeric()
we_nrounds
pasteNQ("Best Params:")
we_params <- cv_best[[2]]
we_params

# best model
we_model <- xgboost(data=we_train, verbose=F,
                    nrounds=we_nrounds, param=we_params)

# prediction
cols <- 22:28
pred_test[ , cols] <- predict(we_model, we_test) %>% 
                     matrix(ncol=num_class, byrow=TRUE)
results_test$WE_Label <- max.col(pred_test[ , cols])

# error and accuracy measure
results_test$WE_Label <- factor(results_test$WE_Label,
                                labels = unique(results_test$Target))
we_acc <- confusionMatrix(results_test$WE_Label, 
                          results_test$Target)
round( we_acc$overall["Accuracy"], 2 )

# Graph
## Balanced Accuracy
we_acc$byClass %>% 
  as.data.frame() %>%
  ggplot(aes(x = `Balanced Accuracy` %>% as.numeric()*100, 
             y = titles, fill = titles)) +
  geom_bar(stat = "identity") +
  xlim(0, 100) +
  labs(title="Balanced Accuracy",
       y="Book",
       x="Balanced Accuracy (%)") + 
  scale_fill_manual(values = c("#946B2D", "#0D6217", "#000A90", 
                               "#AAAAAA", "#000000", "#7F0909", "#FFC500")) +
  Grph_theme()
```


# V) Perform Stacked Ensemble Modeling
**Description:** Ensemble 4 bottom layer models with top layer model
**Purpose:** Take strengths of each model and minimize each model's weaknesses    
     
* Resample train data for each of the 4 models with the same seed to ensure all rows contain same documents across bottom-layer models
* Use 4 training models to generate predicted probabilities and save as seven columns per model in a new data frame (28 columns in total)
* Model bottom layer models with top layer K Nearest Neighbors (KNN) to priviledge model strengths

```{r}
# Topic model 
stm_top_train <- xgb.DMatrix(as.matrix(stm_top_train),
                             label=top_num_train)

# Bag of words TF model
bow_top_train <- xgb.DMatrix(bow_top_train,
                             label=top_num_train)

# Bag of words TF-IDF model
bowtfidf_top_train <- xgb.DMatrix(bowtfidf_top_train,
                                  label=top_num_train)

# Word Embeddings (Sum-SQRT) model
we_top_train <- xgb.DMatrix(we_top_train,
                            label=top_num_train)

# Predicting the bottom layer probabilities
pred_train[ , 1:7]   <- predict(stm_model, stm_top_train) %>% 
                                matrix(ncol=num_class, byrow=TRUE) 

pred_train[ , 8:14]  <- predict(bow_model, bow_top_train) %>% 
                                matrix(ncol=num_class, byrow=TRUE) 

pred_train[ , 15:21] <- predict(bowtfidf_model, bowtfidf_top_train) %>% 
                                matrix(ncol=num_class, byrow=TRUE) 

pred_train[ , 22:28] <- predict(we_model, we_top_train) %>% 
                                matrix(ncol=num_class, byrow=TRUE) 
``` 


## Top Layer (KNN)
```{r}
top_knn_train <- pred_train %>% data.frame()
top_knn_train$target <- top_train_target

# cross validation
trctrl <- trainControl(method = "repeatedcv", number = 4, repeats = 3)
model_top_knn <- train(
  target ~ .,
  data = top_knn_train,
  method = "knn",
  trControl = trctrl,
  preProcess = c("center", "scale"),
  tuneLength = 10
)
top_params <- model_top_knn$bestTune$k

# prediction
results_top_knn_test <- data.frame(matrix(nrow=nrow(test), ncol=7))
results_top_knn_test$Top_KNN_Label <- predict(model_top_knn, pred_test) 

# error and accuracy measure
results_test$Top_KNN_Label <- factor(results_top_knn_test$Top_KNN_Label,
                                     labels = unique(results_test$Target))
top_knn_acc <- confusionMatrix(results_test$Top_KNN_Label, 
                           results_test$Target)
top_knn_acc$overall[1]

# Graph
top_knn_acc$byClass %>% 
  as.data.frame() %>%
  ggplot(aes(x = `Balanced Accuracy` %>% as.numeric()*100, 
             y = titles, fill = titles)) +
  geom_bar(stat = "identity") +
  xlim(0, 100) +
  labs(title="Balanced Accuracy",
       y="Book",
       x="Balanced Accuracy (%)") + 
  scale_fill_manual(values = c("#946B2D", "#0D6217", "#000A90", 
                               "#AAAAAA", "#000000", "#7F0909", "#FFC500")) +
  Grph_theme()
```


# VI) Determine Final Model Performance

**Description:** Test results of stacked model ensemble on testing data
**Purpose:** Ensure model process and outcome is generalizable

```{r}
pasteNQ("Topic Model")
stm_acc$overall["Accuracy"]
cat("\n")

pasteNQ("Bag of Words (TF) Model")
bow_acc$overall["Accuracy"]
cat("\n")

pasteNQ("Bag of Words (TF-IDF) Model")
bowtfidf_acc$overall["Accuracy"]
cat("\n")

pasteNQ("Word Embeddings Model")
we_acc$overall["Accuracy"]
cat("\n")

pasteNQ("Top Layer (KNN) Model")
top_knn_acc$overall["Accuracy"]


# Graph Balanced Accuracy
bal_acc <- cbind(titles, "1 Topic Model", stm_acc$byClass[ , "Balanced Accuracy"]) %>%
     rbind(cbind(titles, "2 Bag of Words (TF)", bow_acc$byClass[ , "Balanced Accuracy"])) %>%
     rbind(cbind(titles, "3 Bag of Words (TF-IDF)", bowtfidf_acc$byClass[ , "Balanced Accuracy"])) %>%
     rbind(cbind(titles, "4 Word Embedding", we_acc$byClass[ , "Balanced Accuracy"])) %>% 
     rbind(cbind(titles, "5 Top Layer", top_knn_acc$byClass[ , "Balanced Accuracy"])) %>% 
  as_tibble()
colnames(bal_acc) <- c("Book", "Model", "Balanced Accuracy")

bal_acc %>% 
  ggplot(aes(x = `Balanced Accuracy` %>% as.numeric()*100, 
             y = Book,
             fill = Model)) +
  geom_bar(stat = "identity") +
  facet_wrap(~Model) +
  labs(title="Balanced Accuracy",
       y="Book",
       x="Balanced Accuracy (%)") + 
  scale_fill_manual(values = c("#0D6217", "#7F0909", "#000A90", "#FFC500", 
                               "#AAAAAA", "#000000")) +
  Grph_theme() 

# Graph COnfusion Matrix
ggplot(results_test, 
       aes(Target, Top_KNN_Label, color=Target)) + 
  geom_jitter(size=1) + 
  labs(title="Confusion Matrix",
       subtitle="Predicted vs. Observed",
       y="Predicted",
       x="Observed") + 
  scale_color_manual(values = c("#946B2D", "#0D6217", "#000A90", 
                               "#AAAAAA", "#000000", "#7F0909", "#FFC500")) +
  Grph_theme() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
```


# Save
```{r}
save(train, test, target_test, 
     pred_train, pred_test, 
     stm_model,
     bow_model, 
     bowtfidf_model, tfidf, 
     we_model, 
     results_test, results_top_knn_test,
     model_top_knn, 
     stm_acc, bow_acc, bowtfidf_acc, we_acc, top_knn_acc,
     file = "Harry_Potter_and_the_Classification_-_Models.RData")

save(pages, para1, para3, 
     stm_func, bow_func, we_func, titles,
     stm_model, stm_nrounds, stm_params,
     bow_model, bow_nrounds, bow_params, 
     bowtfidf_model, bowtfidf_nrounds, bowtfidf_params, 
     we_model, we_nrounds, we_params,    
     file = "Harry_Potter_and_the_Classification_-_Params.RData")
```


