---
title: "Harry Potter NLP"
author: "Michael Siebel"
date: "`r date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    css: "../Rstyles.css" 
    code_folding: hide
    highlight: tango
    includes:
      in_header: "menu.html"
---

<br>

>  Natural Language Processing (NLP) for: <br>
>  Harry Potter and the Philosopher's Stone (1997) <br>
>  Harry Potter and the Chamber of Secrets (1998) <br>
>  Harry Potter and the Prisoner of Azkaban (1999) <br>
>  Harry Potter and the Goblet of Fire (2000) <br>
>  Harry Potter and the Order of the Phoenix (2003) <br>
>  Harry Potter and the Half-Blood Prince (2005) <br>
>  Harry Potter and the Deathly Hallows (2007)

# Bottom Line Up Front

# Setup
```{r, results=FALSE, echo=TRUE, message=FALSE, comment=NA, warning=FALSE, tidy=TRUE} 
rm(list=ls())
gc()


# install.packages("pacman")
# install.packages("remotes")
# library(remotes)
# install.packages("devtools")
# library(devtools)
# remotes::install_github("nrguimaraes/sentimentSetsR")
# library(magrittr)
# devtools::install_github("wch/webshot")
# webshot::install_phantomjs()
# library(BiocManager)
# BiocManager::install("https://bioconductor.org/biocLite.R")
# source("https://bioconductor.org/biocLite.R")
# biocLite("EBImage")
library(pacman)
pacman::p_load(devtools, knitr, magrittr, dplyr, ggplot2, rvest, sentimentSetsR, caret, textTinyR, text2vec, tm, tidytext, stringr, stringi, SnowballC, stopwords, wordcloud, prettydoc, cowplot, kable, utf8, corpus, glue, topicmodels, stm, wordcloud2, htmlwidgets, viridis)
  
knitr::opts_chunk$set(echo=TRUE, message=FALSE, comment=NA, warning=FALSE, tidy=TRUE, results="hold", cache=FALSE, dpi=120)

# Parameters
## N-gram
ngrams <- "single words"
ngram <- c(1, 1)

## Number of Topics
K <- 4

# Custom functions
## Remove quotation marks
pasteNQ <- function(...) {
  output <- paste(...)
  noquote(output)
}
pasteNQ0 <- function(...) {
  output <- paste0(...)
  noquote(output)
}

## Chart Template
Grph_theme <- function() {
  palette <- brewer.pal("Greys", n=9)
  color.background = palette[2]
  color.grid.major = palette[3]
  color.axis.text = palette[6]
  color.axis.title = palette[7]
  color.title = palette[9]    
  theme_bw(base_size=9) + 
  theme(panel.background=element_rect(fill=color.background, color=color.background)) +
  theme(plot.background=element_rect(fill=color.background, color=color.background)) +
  theme(panel.border=element_rect(color=color.background)) +
  theme(panel.grid.major=element_line(color=color.grid.major,size=.25)) +
  theme(panel.grid.minor=element_blank()) +
  theme(axis.ticks=element_blank()) +
  theme(legend.position="none") +
  theme(legend.title=element_text(size=16,color='black')) +
  theme(legend.background = element_rect(fill=color.background)) +
  theme(legend.text = element_text(size=14,color='black')) +
  theme(strip.text.x = element_text(size=14,color='black',vjust=1)) +
  theme(plot.title=element_text(color=color.title, size=20, vjust=1.25)) +
  theme(axis.text.x=element_text(size=14,color='black')) +
  theme(axis.text.y=element_text(size=14,color='black')) +
  theme(axis.title.x=element_text(size=16,color='black', vjust=0)) +
  theme(axis.title.y=element_text(size=16,color='black', vjust=1.25)) +
  theme(plot.margin = unit(c(0.35, 0.2, 0.3, 0.35), "cm"))
}

## Chart Template Facet Wrap
Grph_theme_facet <- function() {
  palette <- brewer.pal("Greys", n=9)
  color.background = palette[2]
  color.grid.major = palette[3]
  color.axis.text = palette[6]
  color.axis.title = palette[7]
  color.title = palette[9]    
  theme_bw(base_size=9) + 
  theme(panel.background=element_rect(fill=color.background, color=color.background)) +
  theme(plot.background=element_rect(fill=color.background, color=color.background)) +
  theme(panel.border=element_rect(color=color.background)) +
  theme(panel.grid.major=element_line(color=color.grid.major,size=.25)) +
  theme(panel.grid.minor=element_blank()) +
  theme(axis.ticks=element_blank()) +
  theme(legend.position="none") +
  theme(legend.title=element_text(size=11,color='black')) +
  theme(legend.background = element_rect(fill=color.background)) +
  theme(legend.text = element_text(size=9,color='black')) +
  theme(strip.text.x = element_text(size=9,color='black',vjust=1)) +
  theme(plot.title=element_text(color=color.title, size=20, vjust=1.25)) +
  theme(axis.text.x=element_text(size=9,color='black')) +
  theme(axis.text.y=element_text(size=9,color='black')) +
  theme(axis.title.x=element_text(size=10,color='black', vjust=0)) +
  theme(axis.title.y=element_text(size=10,color='black', vjust=1.25)) +
  theme(plot.margin = unit(c(0.35, 0.2, 0.3, 0.35), "cm"))
}

## Clean Corpus
basicclean <- function(rawtext) {
  # Set to lowercase
  rawtext <- tolower(rawtext)
  print(pasteNQ("Set to lowercase"))

  # Remove contractions
  fix_contractions <- function(rawtext) {
    rawtext <- gsub("will not", "won't", rawtext)
    rawtext <- gsub("can't", "can not", rawtext)
    rawtext <- gsub("can not", "cannot", rawtext)
    rawtext <- gsub("shant", "shall not", rawtext)
    rawtext <- gsub("n't", " not", rawtext)
    rawtext <- gsub("'ll", " will", rawtext)
    rawtext <- gsub("'re", " are", rawtext)
    rawtext <- gsub("'ve", " have", rawtext)
    rawtext <- gsub("'m", " am", rawtext)
    rawtext <- gsub("'d", " would", rawtext)
    rawtext <- gsub("'ld", " would", rawtext)
    rawtext <- gsub("'ld", " would", rawtext)
    rawtext <- gsub("'s", "", rawtext)
    return(rawtext)
  }
  rawtext <- fix_contractions(rawtext)
  print(pasteNQ("Fixed contractions"))
  
  # Strip whitespace
  rawtext <- stripWhitespace(rawtext)
  print(pasteNQ("Stripped whitespace"))

  return(rawtext)
}

# Remove stop words
removestopwords <- function(rawtext, remove=NULL, retain=NULL) {

  # Remove stop words
  stopwords_custom <- stopwords::stopwords("en", source = "snowball")
  stopwords_custom <- c(stopwords_custom, remove)
  stopwords_retain <- retain
  stopwords_custom <- stopwords_custom[!stopwords_custom %in% stopwords_retain]
  rawtext <- removeWords(rawtext, stopwords_custom)
  print(pasteNQ("Removed", length(stopwords_custom), "stop words"))
  
  return(rawtext)
}

## Word Stemming
wordstem <- function(rawtext) {
  # Stemming words
  rawtext <- stemDocument(rawtext)
  print(pasteNQ("Stemmed words"))
  
  return(rawtext)
}

## Remove Non-Alpha
removenonalpha <- function(rawtext) {
  # Remove puncutation, numbers, and other none characters
  rawtext <- removePunctuation(rawtext)
  rawtext <- removeNumbers(rawtext)
  rawtext <- gsub("[^[:alnum:]///' ]", "", rawtext)
  rawtext <- gsub("[']", "", rawtext)
  print(pasteNQ("Removed punctuation, numbers, and other none characters"))
  
  return(rawtext)
}

# Remove JavaScript from WordClouds
library("EBImage")
embed_htmlwidget <- function(widget, rasterise = T) {
  outputFormat = knitr::opts_knit$get("rmarkdown.pandoc.to")
  if(rasterise || outputFormat == 'latex') {
    html.file = tempfile("tp",fileext=".html")
    png.file = tempfile("tp",fileext=".png")

    htmlwidgets::saveWidget(widget, html.file, selfcontained = FALSE)
    webshot::webshot(html.file, file = png.file,vwidth = 700, vheight = 500, delay =10)
    img = EBImage::readImage(png.file)
    EBImage::display(img)
  } else {
    widget
  }
}
```


## Load Data

```{r}
setwd("C:/Users/siebe/Documents/07_Books/Harry Potter/")

titles <- c("Philosopher's Stone", "Chamber of Secrets", "Prisoner of Azkaban",
            "Goblet of Fire", "Order of the Phoenix", "Half-Blood Prince",
            "Deathly Hallows")
html <- c("Harry_Potter_and_the_Philosophers_Stone.html",
          "Harry_Potter_and_the_Chamber_of_Secrets.html",
          "Harry_Potter_and_the_Prisoner_of_Azkaban.html",
          "Harry_Potter_and_the_Goblet_of_Fire.html",
          "Harry_Potter_and_the_Order_of_the_Phoenix.html",
          "Harry_Potter_and_the_Half-Blood_Prince.html",
          "Harry_Potter_and_the_Deathly_Hallows.html")

para3 <- tibble(Text=as.character(), Book=as.character())
para1 <- tibble(Text=as.character(), Book=as.character())
books <- tibble(Text=as.character(), Book=as.character())

for (i in 1:7) {  
  rawtext <- read_html(html[i])%>%
      html_nodes(xpath = '/html/body/p') %>%
          html_text(trim = TRUE)
  
  wordcount <- sapply(strsplit(rawtext, " "), length)
  paragraph <- rawtext[wordcount > 2]
  
  para1 <- rbind(para1, 
                 tibble(Text = paragraph,
                            Book = titles[i])
           )
  
  books <- rbind(books,
                 tibble(Text = str_c(paragraph, 
                                         collapse = " "),
                            Book = titles[i]
                            )
           )

  triplet <- do.call(rbind, 
                     lapply(seq(1, length(paragraph), by = 3),
                          function(x) 
                                  tibble(Text = str_c(paragraph[x:(x+2)], 
                                                          collapse = " "),
                                             Book = titles[i]
                                             )
                          )
                   )
  para3 <- rbind(para3, triplet)
}

pages <- books %>%
  unnest_tokens(Text, Text, strip_punct = T, to_lower = F) %>%
  group_by(Book, Page = dplyr::row_number() %/% 250) %>%
  dplyr::summarize(Text = stringr::str_c(Text, collapse = " ")) %>%
  mutate(Page = dplyr::row_number()) %>%
  ungroup()

para3$Book <- factor(para3$Book, levels=titles)
books$Book <- factor(books$Book, levels=titles)
pages$Book <- factor(pages$Book, levels=titles)
```


# Sentiment of Book

## Sentiment Scores
```{}
# Sentiment Scores
average <- function(x) {
  pos <- sum(x[x>0], na.rm = T)
  neg <- sum(x[x<0], na.rm = T) %>% abs()
  neu <- length(x[x==0])
  bal <- ( (pos-neg)/(pos+neg) )*100
  y <- ifelse(is.nan(bal),0,bal)
  return(y)
}
books$Text <- basicclean(books$Text)
books$Score <- sapply(books$Text, 
                            function(x) getSentiment(x, dictionary = "vader", 
                                                     score.type = average))
pasteNQ("")
pasteNQ("Overall Sentiment")
mean(books$Score)
```


## Graph Sentiment of Books
```{}
# Graph
books %>%
  mutate(Book=factor(Book, levels=Book),
         Sentiment=Score) %>% 
    ggplot(aes(x=Book, y=Sentiment %>% as.numeric() %>% round(1), fill=Book))+
        geom_col()+
        coord_flip()+
        Grph_theme_facet()+
        ylab("Sentiment (-100% to 100%)")+
        xlab("") + ggtitle("Sentiment of Books") + 
        scale_fill_manual(values = c("#946B2D", "#0D6217", "#000A90", 
                                 "#AAAAAA", "#000000", "#7F0909", "#FFC500"))
        guides(fill=FALSE) 
```

## Bigram Network Analysis
```{}
book_sent <- para3[ , c("Book", "Score")]

book_sent %>%
  group_by(Book) %>% 
  mutate(Paragraph=row_number()) %>% 
  ggplot(aes(Paragraph, Score, fill = Book)) +
  Grph_theme_facet()+
  geom_bar(alpha = 0.5, stat = "identity", show.legend = FALSE) +
  facet_wrap(~ Book, ncol = 2, scales = "free_x")

book_bigram <- para3_text %>% 
  unnest_tokens(Bigram, Text, token = "ngrams", n = 2) %>%
  tidyr::separate(Bigram, c("word1", "word2"), sep = " ") %>%
  dplyr::filter(!word1 %in% stop_words$word) %>%
  dplyr::filter(!word2 %in% stop_words$word) %>%
  dplyr::count(Book, word1, word2, sort = TRUE) 

library(igraph)
bigram_graph <- book_bigram %>%
  filter(n > 100) %>%
  graph_from_data_frame()

library(ggraph)
set.seed(20)
ggraph(bigram_graph, layout = "fr") +
  Grph_theme()+
  geom_edge_link() +
  geom_node_point() +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1)
```

# Sentiment of Films

```{}
folder <- "C:/Users/siebe/Documents/01_R/Harry Potter/"

scripts <- c("HP_Script_1.txt",
             "HP_Script_2.txt",
             "HP_Script_3.txt",
             "HP_Script_4.txt",
             "HP_Script_5.txt",
             "HP_Script_6.txt",
             "HP_Script_7.txt",
             "HP_Script_8.txt")
film_titles <- c(titles, "Deathly Hallows Part II")

films <- data.frame(Text=as.character(), Film=as.character())

for(i in 1:8) {
  con <- file(paste0(folder, scripts[i]), open = "r")
  rawtext <- readLines(con)
  
  films <- rbind(films,
                 data.frame(Text = rawtext,
                            Film = film_titles[i]
                            )
           )
}
```


## Sentiment Scores
```{}
# Sentiment Scores
average <- function(x) {
  pos <- sum(x[x>0], na.rm = T)
  neg <- sum(x[x<0], na.rm = T) %>% abs()
  neu <- length(x[x==0])
  bal <- ( (pos-neg)/(pos+neg) )*100
  y <- ifelse(is.nan(bal),0,bal)
  return(y)
}
films$Text <- basicclean(films$Text)
films$Score <- sapply(films$Text, 
                           function(x) getSentiment(x, dictionary = "vader", 
                                                    score.type = average)) 

pasteNQ("")
pasteNQ("Overall Sentiment")
round(mean(films$Score), 1)
films[ , c("Film", "Score")]
```


## Graph Sentiment of Films
```{}
# Graph
books %>%
  mutate(Book=factor(Book, levels=Book),
         Sentiment=Score) %>% 
    ggplot(aes(x=Book, y=Sentiment %>% as.numeric() %>% round(1), fill=Book))+
        geom_col()+
        coord_flip()+
        Grph_theme_facet()+
        ylab("Sentiment (-100% to 100%)")+
        xlab("") + ggtitle("Sentiment of Films") + 
        scale_fill_manual(values = c("#946B2D", "#0D6217", "#000A90", 
                                 "#AAAAAA", "#000000", "#7F0909", "#FFC500", "Black"))
        guides(fill=FALSE) 
```


# Sentiment of Paragraph (Triplets)

## Word Distributions

The distributions are similar across books, making it a comparable level of analysis.

```{r}
para3$Wordcount <- sapply(strsplit(para3$Text %>% as.character(), " "), length)

pasteNQ0("Average Amount of Words per Paragraph Triplet")
summary(para3$Wordcount)

# Graph distribution of words all
ggplot(para3, aes(Wordcount, fill=I("maroon"))) + 
  geom_histogram() + 
  stat_bin(bins = 100) +
  Grph_theme() +
  ylab('Frequency') + xlab('Count of Words') + 
  ggtitle('Words per Paragraph Triplet')

# Graph with book fill
ggplot(para3, aes(Wordcount, fill=Book)) + 
  geom_area(stat = "bin") + 
  scale_fill_manual(values = c("#946B2D", "#0D6217", "#000A90", 
                                 "#AAAAAA", "#000000", "#7F0909", "#FFC500")) +
  Grph_theme() +
  ylab('Frequency') + xlab('Count of Words') + 
  ggtitle('Words per Paragraph Triplet') + 
  theme(legend.text = element_text(size=8,color='black')) +
  theme(legend.position="bottom")
```


## Heroes and Villians

```{r}
# Create Dictionaries
trio <- c("harry","ron","hermione")
pasteNQ("Main Characters:")
paste(trio)
cat("\n")

heroes <- c("lily","james","hagrid","dumbledore","sirius","lupin","moody","slughorn","dobby","cedric","luna","tonks","mcgonagall","ginny","order of the phoenix","neville")
pasteNQ("Number of Heroes:", length(heroes))
pasteNQ("Including:")
paste(heroes)
cat("\n")

villians <- c("snape","draco","lucius","umbridge","voldemort","quirrell","pettigrew","dementor","greyback","bellatrix","dudley","vernon","petunia","riddle","death eaters","aragog","basilisk","nagini","dementors")
pasteNQ("Number of Villians:", length(villians))
pasteNQ("Including:")
paste(villians)
```


## Sentiment Scores

```{r}
# Sentiment Scores
average <- function(x) {
  pos <- sum(x[x>0], na.rm = T)
  neg <- sum(x[x<0], na.rm = T) %>% abs()
  neu <- length(x[x==0])
  bal <- ( (pos-neg)/(pos+neg) )*100
  y <- ifelse(is.nan(bal),0,bal %>% as.numeric())
  return(y)
}
CleanText <- basicclean(para3$Text)
para3$Score <- sapply(CleanText, 
                      function(x) getSentiment(x, dictionary = "vader", 
                                               score.type = average)) 
para3$Cross <- NA
para3$Cross <- ifelse(para3$Score<0, "Negative", para3$Cross)
para3$Cross <- ifelse(para3$Score>0, "Positive", para3$Cross)
para3$Cross <- ifelse(para3$Score==0, "Neutral", para3$Cross)
pasteNQ("Sentiment Levels")
table(para3$Cross)
```


## Graph Sentiment of Main Trio

```{r}
# Subset text mentioning a main character
trio_sent <- data.frame(Trio=NA, 
                        Sentiment=NA)

# Find mean of sentiment scores for each main character and
# create ID of all trio for total row
trio_ID <- c()
for(string in trio) {
  findstr <- paste0("\\b",string,"\\b")
  trio_sent <- rbind(trio_sent, 
                       c(string, 
                         para3 %>%
                           as.data.frame() %>%
                           .[grepl(findstr,CleanText),"Score"] %>%
                             average() %>% as.numeric()
                       )
  )
  trio_ID <- c(trio_ID, grep(findstr,CleanText))
}

# Sort data
trio_sent <- trio_sent %>%
               .[order(trio_sent$Sentiment %>% as.numeric()),] %>%
               tidyr::drop_na()
max_sent <- max(trio_sent$Sentiment %>% as.numeric() %>% abs()+1) 

# Add main character total
trio_ID <- unique(trio_ID)
trio_sent <- rbind(trio_sent, c("average of trio",
                                    para3 %>%
                                      as.data.frame() %>%
                                      .[trio_ID,"Score"] %>%
                                        average() %>% as.numeric()
                                  )
               )

# Graph
trio_sent %>%
  mutate(Trio=factor(Trio, levels=Trio)) %>% 
    ggplot(aes(x=Trio, y=Sentiment %>% as.numeric() %>% round(1), fill=Trio))+
        geom_col()+
        coord_flip()+
        Grph_theme_facet()+
        ylab("Sentiment (-100% to 100%)")+
        xlab("") + ggtitle("Sentiment of trio") + 
        ylim(max_sent*-1, max_sent) + 
        scale_fill_manual(values = c("#FFC500", "#AAAAAA", "#7F0909", 
                                     "black")) +
        guides(fill=FALSE) 
```


## Graph Sentiment of Heroes
```{r}
# Subset text mentioning a hero
heroes_sent <- data.frame(Hero=NA, 
                          Sentiment=NA)

# Find mean of sentiment scores for each hero and
# create ID of all heroes for total row
heroes_ID <- c()
for(string in heroes) {
  findstr <- paste0("\\b",string,"\\b")
  heroes_sent <- rbind(heroes_sent, 
                       c(string, 
                         para3 %>%
                           as.data.frame() %>%
                           .[grepl(findstr,CleanText),"Score"] %>%
                             average() %>% as.numeric()
                       )
  )
  heroes_ID <- c(heroes_ID, grep(findstr,CleanText))
}

# Sort data
heroes_sent <- heroes_sent %>%
               .[order(heroes_sent$Sentiment %>% as.numeric()),] %>%
               tidyr::drop_na()
max_sent <- max(heroes_sent$Sentiment %>% as.numeric() %>% abs()+1) 

# Add hero total
heroes_ID <- unique(heroes_ID)
heroes_sent <- rbind(heroes_sent, c("average of heroes",
                                    para3 %>%
                                      as.data.frame() %>%
                                      .[heroes_ID,"Score"] %>%
                                        average() %>% as.numeric()
                                  )
               )

# Graph
heroes_sent %>%
  mutate(Hero=factor(Hero, levels=Hero)) %>% 
    ggplot(aes(x=Hero, y=Sentiment %>% as.numeric() %>% round(1), fill=Hero))+
        geom_col()+
        coord_flip()+
        Grph_theme_facet()+
        ylab("Sentiment (-100% to 100%)")+
        xlab("") + ggtitle("Sentiment of Heroes") + 
        ylim(max_sent*-1, max_sent) + 
        scale_fill_manual(values = c(viridis(nrow(heroes_sent)-1),
                                     "black")) +
        guides(fill=FALSE) 
```


## Graph Sentiment of Villians
```{r}
# Subset text mentioning a villian
villians_sent <- data.frame(Villian=NA, 
                            Sentiment=NA)

# Find mean of sentiment scores for each villian and
# create ID of all villians for total row
villians_ID <- c()
for(string in villians) {
  findstr <- paste0("\\b",string,"\\b")
  villians_sent <- rbind(villians_sent, 
                         c(string, 
                           para3 %>%
                             as.data.frame() %>%
                             .[grepl(findstr,CleanText),"Score"] %>%
                               average() %>% as.numeric()
                         )
  )
  villians_ID <- c(villians_ID, grep(findstr,CleanText))
}

# Sort data
villians_sent <- villians_sent %>%
               .[order(villians_sent$Sentiment %>% as.numeric()),] %>%
               tidyr::drop_na()
max_sent <- max(villians_sent$Sentiment %>% as.numeric() %>% abs()+1) 

# Add hero total
villians_ID <- unique(villians_ID)
villians_sent <- rbind(villians_sent, c("average of villians",
                                        para3 %>%
                                          as.data.frame() %>%
                                          .[villians_ID,"Score"] %>%
                                            average() %>% as.numeric()
                                      )
               )

# Graph
villians_sent %>%
  mutate(Villian=factor(Villian, levels=Villian)) %>% 
    ggplot(aes(x=Villian, y=Sentiment %>% as.numeric() %>% round(1), fill=Villian))+
        geom_col()+
        coord_flip()+
        Grph_theme_facet()+
        ylab("Sentiment (-100% to 100%)")+
        xlab("") + ggtitle("Sentiment of Villians") + 
        ylim(max_sent*-1, max_sent) + 
        scale_fill_manual(values = c(viridis(nrow(villians_sent)-1),
                                     "black")) +
        guides(fill=FALSE) 
```


## Sentiment of Characters Across Books

```{r}
# Main Characters Sentiment
trio_grp <- para3[trio_ID,] %>%
  mutate(Negative = recode(Cross, Positive = 0, Neutral = 0, Negative = 1),
         Neutral = recode(Cross, Positive = 0, Neutral = 1, Negative = 0)) %>%
  group_by(Book) %>%
  summarize(`Trio Sentiment` = mean(Negative, na.rm=T)*100) 

# Heroes Sentiment
heroes_grp <- para3[heroes_ID,] %>%
  mutate(Negative = recode(Cross, Positive = 0, Neutral = 0, Negative = 1),
         Neutral = recode(Cross, Positive = 0, Neutral = 1, Negative = 0)) %>%
  group_by(Book) %>%
  summarize(`Heroes Sentiment` = mean(Negative, na.rm=T)*100) 

# Villians Sentiment
villians_grp <- para3[villians_ID,] %>%
  mutate(Negative = recode(Cross, Positive = 0, Neutral = 0, Negative = 1),
         Neutral = recode(Cross, Positive = 0, Neutral = 1, Negative = 0)) %>%
  group_by(Book) %>%
  summarize(`Villians Sentiment` = mean(Negative, na.rm=T)*100) 

# Plot
df <- inner_join(heroes_grp, villians_grp, by = "Book") %>% as_tibble()
df <- inner_join(trio_grp, df, by = "Book") 
colors <- c("Heroes" = "maroon", "Villians" = "forestgreen", 
            "Main Trio" = "#FFC500")
ggplot(df, mapping = aes(x=Book, group=NA)) +
  geom_line(aes(y = `Trio Sentiment`, color = "Main Trio"), size = 3) +
  geom_line(aes(y = `Heroes Sentiment`, color = "Heroes"), size = 1.5) +
  geom_line(aes(y = `Villians Sentiment`, color = "Villians"), size = 1.5) +
  ggtitle("Sentiment of Heroes and Villians Across Books") +
  Grph_theme_facet() +
  scale_color_manual(values = colors) +
  theme(axis.text.x=element_text(size=8, angle=45)) +
  theme(legend.position="right") +
  ylim(0, 60) +
  labs(x = "Books",
       y = "Negative Sentiment (%)",
       color = "Legend") 

    
```


# Page

## Sentiment Scores
```{r}
# Sentiment Scores
average <- function(x) {
  pos <- sum(x[x>0], na.rm = T)
  neg <- sum(x[x<0], na.rm = T) %>% abs()
  neu <- length(x[x==0])
  bal <- ( (pos-neg)/(pos+neg) )*100
  y <- ifelse(is.nan(bal),0,bal %>% as.numeric())
  return(y)
}
CleanText <- basicclean(pages$Text)
pages$Score <- sapply(CleanText, 
                      function(x) getSentiment(x, dictionary = "vader", 
                                               score.type = average)) 
pages$Cross <- NA
pages$Cross <- ifelse(pages$Score<0, "Negative", pages$Cross)
pages$Cross <- ifelse(pages$Score>0, "Positive", pages$Cross)
pages$Cross <- ifelse(pages$Score==0, "Neutral", pages$Cross)
pasteNQ("Sentiment Levels")
table(pages$Cross)
```


## Sentiment by Page

```{r}
pages %>%
  group_by(Book) %>% 
  mutate(Paragraph=row_number()) %>% 
  ggplot(aes(Page, Score, fill = Book)) +
  Grph_theme_facet() +
  geom_bar(alpha = 0.5, stat = "identity", show.legend = FALSE) +
  facet_wrap(~ Book, ncol = 2, scales = "free_x")
```